BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-06 tex/3-algorithms.tex

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding we page as well as target content such as the article, it's title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

% textual pseudocode
\autoref{extractionAlgo} show the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \ref{timecomplexityandlinearreformulation} we analyses time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

>>>>

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

% textual pseudocode
\autoref{extractionAlgo} shows the generic procedure we use to build extraction rules. The idea is quite simple: for each \code{(}\emph{page, target}\code{)} input, compute out of all possible extraction rules the best one with respect to a certain \code{ScoreFunction}. The rule which is most frequently a \emph{best rule} is then returned.

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in details in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \ref{timecomplexityandlinearreformulation} we analyse time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.
